### 2008-08-12 doc/backend_interface/Backends-arc1.tex
backends docs update

This document describes the next generation Advanced Resource Connector~\cite{arc1} (ARC)
batch system back-end infrastructure. It aims to describe the infrastructure
in enough detail that a developer can add a new local resource management
system (LRMS) to the ARC middleware. It also intends to serve as a
reference manual describing existing batch system interfaces. Note
that the current solution described in this manual is not a real interface,
it is too diffuse to be that.

@@

\begin{enumerate}
\item to allow the GridManager (GM), which is resided in A-REX, to manipulate
jobs in the LRMS including job submit, cancel operations etc.
\item to collect information about jobs, users, the batch system and the cluster
itself for the Information System. 
\end{enumerate}
The former will be referred to as the job control back-end interface
while the latter is the information system interface of the batch
system back-ends. These two will be treated separately in the following
sections.

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Comments \\
\hline \hline
BaseType & \texttt{Share} \\
\hline
Name & from the configuration \\
\hline
Description & ``comment'' configuration option \\
\hline
MappingQueue & from the configuration \\
\hline
SchedulingPolicy & if MAUI is used, set to \texttt{fairshare} \\
\hline
ServingState & has the same value as ComputingEndpoint.ServingState \\
\hline
\end{tabular}

>>>>

This document describes the next generation Advanced Resource Connector~\cite{arc1} (ARC)
batch system back-end infrastructure. It aims to describe the infrastructure
in enough detail that a developer can add a new local resource management
system (LRMS) to the ARC middleware. It also intends to serve as a
reference manual describing existing batch system interfaces.  Note that
certain details of the interface which are not yet finalized are not described,
but will be included in a future revision of this document.

@@

\begin{enumerate}
\item to allow the GridManager (GM), which is resided in A-REX, to control
jobs in the LRMS including job submit, cancel operations etc.
\item to collect information about jobs, users, the batch system and the cluster
itself for the Information System. 
\end{enumerate}
The former will be referred to as the job control back-end interface
while the latter is the information system interface of the batch
system back-ends. These two will be treated separately in the following
sections.

@@

\begin{tabular}{|l|p{12cm}|}
\hline
Property & Comments \\
\hline \hline
BaseType & \texttt{Share} \\
\hline
Name & `name'' configuration option \\
\hline
Description & ``comment'' configuration option \\
\hline
MappingQueue & ``lrms\_queue'' configuration option \\
\hline
SchedulingPolicy & if MAUI is used, it is set to \texttt{fairshare} \\
\hline
ServingState & has the same value as ComputingEndpoint.ServingState \\
\hline
\end{tabular}
